ms_5

### 2020-04-26 ms_5.Rmd
fixed col spec- only error is NAs introcued by coercion

death_by_year_and_state <- read_csv("Drug Overdose Deaths by Year and State.csv", 
                                    col_types = "lcdccddddc")

@@

countypop <- read_csv("countypop.csv",
                      col_types = "cd") %>%
  mutate(Pop = Pop/100000) %>%
  rename(subregion = CTYNAME) %>%
  mutate(subregion = tolower(subregion)) %>%
  select(subregion, Pop)

>>>>

death_by_year_and_state <- read_csv("Drug Overdose Deaths by Year and State.csv", 
                                    col_types = "lcdccddddc") %>%
  filter(`Crude Rate` != "Unreliable")

@@

countypop <- read_csv("countypop.csv",
                      col_types = "cdd") %>%
  mutate(Pop = Pop/100000) %>%
  rename(subregion = CTYNAME) %>%
  mutate(subregion = tolower(subregion)) %>%
  select(subregion, Pop)
